\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Yang Wang}
\address{ 196 Tiber Way \\ St Charles, MO 63301 }
\address{ +1-765-637-6099 \\
  \href{mailto:purduewang@gmail.com}{purduewang@gmail.com} \\
  \href{https://waterkingwatergoat.com/}{waterkingwatergoat.com}}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf Purdue University, West Lafayette} \hfill {Aug. 2015 -- Jun. 2021}
    \\
    {Ph.D. in Electrical Engineering} \\
    \textit{Thesis: Design and Implementations of Open-Source Ag IoT Devices \\
      for Farm Machinery Data Acquisition and Integrated Analytics}

    {\bf Purdue University, West Lafayette} \hfill {Aug. 2010 -- Dec. 2014}
    \\
    {B.S. in Electrical Engineering} \\
  \end{rSection}

  \begin{rSection}{Experience}
    \begin{rSubsection}{The Climate Corporation}{Nov. 2022 --
      Present}{Senior Data Scientist}{St Louis, MO}
      \item Lead the development of a Python package that transformed a vector
        layer with continuous planting attributes into a layer that
        provided up to 10x data size reduction with minimal loss of
        fidelity.
      \item Co-lead the development and deployment of a Python package that cut
        the reliance of an error-prone 3rd-party service for translating
        vendor-specific Shapefiles. The package boosted translation success
        rate from 50\% to 95\%.
      \item Key contributor to various internal spatial pipeline components
        that transform customer spatiotemporal data into usable artifacts for
        internal teams.
      \item Founded a working group on farm machinery data and lead monthly
        knowledge sharing sessions. Doubled the number of
        participants in one quarter.
    \end{rSubsection}

    \begin{rSubsection}{John Deere Intelligent Solutions Group}{Jul. 2021 --
      Oct. 2022}{Senior Navigation Engineer}{Torrance, CA}
      \item Refactored legacy C++ codebases and implemented bug fixes for GNSS
        receiver (StarFire) firmware.
    \end{rSubsection}

    \begin{rSubsection}{Purdue University}{Aug. 2015 -- Jun. 2021}{Graduate
        Research / Teaching Assistant}{West Lafayette, IN}
      \item Processed GNSS tracks from ag machinery with Kalman filtering and
        spatiotemporal clustering algorithms for track classification and
        harvest productivity analyses across multiple years and machines.
      \item Designed and wrote software for 10+ telematics units (ISOBlue 2)
        for automatic CAN, GNSS, and video data collection for ag machinery.
        Deployed these units domestically and internationally through
        coordinations with farmers and machine operators.
    \end{rSubsection}

    \begin{rSubsection}{Spensa Technologies Inc. (Acquired by DTN)}{Jan. 2015 --
      May. 2015}{Embedded Systems Engineer}{West Lafayette, IN}
      \item Implemented embedded firmware and assisted with PCB layout for new
        base station launch.
    \end{rSubsection}

%    \begin{rSubsection}{Spensa Technologies Inc.}{May. 2014 --
%        Dec. 2014}{Embedded Engineer Internship}{West Lafayette, IN}
%      \item Ported and tested legacy firmware to new hardware platform.
%    \end{rSubsection}
%
%    \begin{rSubsection}{Keithley Instruments, LLC.}{Aug. 2012 --
%        Dec. 2012}{Test Engineer Internship}{Cleveland, OH}
%      \item Implemented faster test automation programs for auditing existing
%        products.
%      \item Troubleshooted and documented faulty products using oscilloscopes
%        and DMMs.
%    \end{rSubsection}
  \end{rSection}

  \begin{rSection}{Core Competencies}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Languages & Python, C, C++, MATLAB, Shell scripting, \LaTeX,
      Java, Javascript \\
      Cloud \& Infrastructure & AWS \& GCP (both with limited proficiency) \\
      Parallel Processing & PySpark \\
      Embedded Systems & Yocto Linux, Android, ISOBUS VT \\
      Network \& Messaging Protocols & CAN, J1939, ISOBUS, MQTT, Apache Kafka \\
      Databases & MySQL, TimescaleDB, DuckDB \\
      Observability & Datadog, OpenSearch, Splunk \\
      Version Control Systems & Git, Team Foundation Server \\
      Languages & English and Mandarin (both fluent), French (limited proficiency) \\
    \end{tabular}
  \end{rSection}

%  \begin{rSection}{Recent Award}
%    \textbf{2024 ASABE Superior Paper Award} --- \textit{A Methodology for
%    Combine Performance Analyses in Wheat Harvests with GNSS Data}.
%  \end{rSection}

\end{document}
